DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-30 paper/overview.tex
intro revision
Minor changes to overview

For the neural network architecture, we adopt a TensorFlow version of
NVIDIA DAVE-2's convolutional neural network (CNN), published by Dr.
Fridman at  MIT~\footnote{https://github.com/lexfridman/deeptesla}. As
in DAVE-2, the CNN takes a raw color image (200x66 RGB pixels)
as input and produces a single steering angle value as
output. Figure~\ref{fig:architecture} shows the network architecture, which
is comprised of 8 layers, 250K parameters, and about 27 million
connections.

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 8 layers (5
    convolutional, 3 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

Despite these issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained. The source code, build
instruction, and a collection of self-driving videos of the DeepPicar
can be found at: \url{https://github.com/heechul/picar}.

>>>>

For the neural network architecture, we adopt a TensorFlow version of
NVIDIA DAVE-2's convolutional neural network (CNN), published by Dr.
Fridman at  MIT~\footnote{https://github.com/lexfridman/deeptesla}. The 
main difference is that we do not utilize a normalization layer, and 
instead initialize the weights using a Xavier initialization. As
in DAVE-2, the CNN takes a raw color image (200x66 RGB pixels)
as input and produces a single steering angle value as
output. Figure~\ref{fig:architecture} shows the network architecture, which
is comprised of 8 layers, 250K parameters, and about 27 million
connections.

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 8 layers (5
    convolutional, 3 fully-connected layers), 27 million connections,
    250K parameters. The architecture is almost identical to the one 
	used in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

Despite these issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained.
